Reproducible Research in R: A Tutorial on How to Do the Same Thing More {Than Once}

### 2022-04-04 manuscript.tex

%=================================================================
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
\externaleditor{Academic Editor: {Alexander Robitzsch}}
\datereceived{} 
\dateaccepted{} 
\datepublished{}
\hreflink{https://doi.org/} % If needed use \linebreak

@@

\AuthorCitation{Peikert, A.;  van Lissa, J.; Brandmaier, A.M.}
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Center for Lifespan Psychology---Max Planck Institute for Human Development, Lentzeallee 94, \mbox{14195 Berlin, Germany;} brandmaier@mpib-berlin.mpg.de\\
$^{2}$ \quad Humboldt-Universität zu Berlin, Unter den Linden 6, \mbox{10117 Berlin, Germany}

$^{3}$ \quad \hl{Department} of Methodology \& Statistics---Utrecht {University}, {Faculty} of Social and Behavioral Sciences
, Heidelberglaan 8, 3584 CS Utrecht, The Netherlands; C.J.vanLissa@uu.nl\\
$^{4}$ \quad Open Science Community Utrecht, Heidelberglaan 8, 3584 CS Utrecht, The Netherlands\\
$^{5}$ \quad Max Planck UCL Centre for Computational Psychiatry and Ageing Research, \mbox{\hl{Lentzeallee 94
14195 Berlin, Germany, and London, WC1B 5EH, UK}}\\
$^{6}$ \quad MSB Medical School Berlin, Rüdesheimer Str. 50, 14197 Berlin, Germany}

@@

Dynamic document generation integrates both steps. Through dynamic
document generation, code becomes an integral, although usually hidden,
part of the manuscript, complementing the verbal description and
allowing interested readers to gain a deeper understanding of the
contents
\citep{knuthCWEBSystemStructured, claerboutElectronicDocumentsGive1992}.
\texttt{R\ Markdown} uses \texttt{Markdown} for text formatting and R
(or other programming languages) for writing the statistical analysis.
\texttt{Markdown} is a lightweight text format in plain text with a
minimal set of reserved symbols for formatting instructions. This way,
\texttt{Markdown} does not need any specialized software for editing. It
is userfriendly (unlike, for example, \texttt{LaTeX}
\citep{lamportLATEXDocumentPreparation1994}), works well with version
control systems, and can be exported to various document formats, such
as HTML websites, a Microsoft Word document, a typeset PDF file (for
example, via LaTeX journal templates), or a Powerpoint presentation.
\texttt{Markdown} can be used for all sorts of academic documents,
ranging from simple sketches of ideas to scientific manuscripts
\citep{R-rticles} and presentations~\citep{revealjs}, or even résumés
\citep{vitae}. \texttt{R\ Markdown} extends regular \texttt{Markdown} by
allowing users to include R code chunks (in fact, arbitrary computer
code \citep[Chapter 15, Chapter 15, Other
Languages]{xieMarkdownCookbook2020}) into a \texttt{Markdown} document.
Upon rendering the document, the code blocks are executed, and their
output is dynamically inserted into the document. This allows the
creation of (conditionally) formatted text, statistical results, and
figures that are guaranteed to be up-to-date because they are created
anew every time the document is rendered to its output format (e.g.,
presentation slides or a journal article).
Xie et al.~\citep{xieMarkdownCookbook2020} provides an extensive yet practical
introduction to most features of \texttt{R\ Markdown}.

@@

\begin{figure}[H]
%\centering
\includegraphics[width=13.5cm]{Figures/nutshell.pdf}
\caption{Schematic illustration of the interplay of the four
components (in dashed columns) central to the reproducible workflow:
version control (\texttt{Git}), dependency tracking (\texttt{Make}),
software management (\texttt{Docker}), and dynamic document generation
(\texttt{R\ Markdown}). \texttt{Git} tracks changes to the project over
time. \texttt{Make} manages dependencies among the files.
\texttt{Docker} provides a container in which the final report is built
using dynamic document generation in \texttt{R\ Markdown}. Adapted from
Peikert and Brandmaier~\citep{Peikert2019} licensed under CC BY 4.0 
(\url{https://creativecommons.org/licenses/by/4.0}).}
\label{figure1}
\end{figure}

@@

The first step is to install the required software. We assume that you
have installed R (\citep{R-base} version 4.0.4) and RStudio
(\citep{rstudio} version 1.4) already but the tutorial will guide you in
detail through the installation of other necessary software with the
help of the R package {\texttt{repro}} 
(\url{https://github.com/aaronpeikert/repro})~\citep{R-repro}. In case you have either not installed R and RStudio or
are unsure if they are up-to-date, you might want to consult our
installation advice in the Online Supplementary Material
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md}) that covers the installation of all software
necessary for this tutorial in three steps. The
{installation advice}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md} accessed on 11 October 2021) may also help Windows users who have problems installing
\texttt{Docker}.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  Text (prose; e.g., a scientific paper or presentation)
\item
  Executable code (e.g., analyses)
\item
  Metadata (e.g.~title, authors, document format)
\end{enumerate}

@@

One advantage of this type of markup for formatting is that it can be
rendered to many different output formats---both in terms of file types,
like \texttt{.docx}, \texttt{.html}, \texttt{.pdf}, and in terms of
style, e.g.~specific journal requirements. For social scientists, the
\href{https://github.com/crsh/papaja}{\texttt{papaja}} package
\citep{papaja} may be relevant, as it produces manuscripts that follow
the American Psychological Association formatting requirements
\citep{apa7}. \texttt{R\ Markdown} files are plain text, which is more
suitable for version control using \texttt{Git} than binary files
generated by some word processors. Some users might find it easier to
activate the ``Visual Editor'' of RStudio ({[}Ctrl{]} + {[}Shift{]} +
{[}F4{]} or click on the icon that resembles drawing materials or a
compass in the upper right corner of the \texttt{R\ Markdown} document),
which features more graphical elements like a traditional word processor
but still creates an \texttt{R\ Markdown} underneath with all of its
flexibility. The visual editor has some additional benefits, such as
promoting best practices (for example, each sentence should be written
on a new line, which makes it easier to track changes across versions)
and improving the generation of citations and references to tables and
figures.

@@

The hotkey {[}Control{]}+{[}Alt{]}+{[}i{]} inserts a block of code in
the file. The results of code enclosed in such backticks will be
dynamically inserted into the document (depending on specific settings).
This means that whenever you render the \texttt{R\ Markdown} to its
intended output format, the code will be executed and the results
updated. The resulting output document will be static, e.g., a pdf
document, and can be shared wherever you like, e.g., on a preprint
server.

@@

The workflow described in this paper facilitates a rigorous solution to
this problem: Instead of describing the analysis in prose, researchers
include the code required to conduct the analysis in the
preregistration. We term this approach of writing and publishing code at
the preregistration stage \emph{Preregistration as Code (PAC)}. PAC has
the potential to eliminate undisclosed researchers degrees of freedom to
a much greater extent than, e.g., preregistration templates. Moreover,
it reduces overhead by removing the need to write a separate
preregistration and manuscript. For PAC, researchers can write a
reproducible, dynamically generated draft of their intended manuscript
at the preregistration stage. This already includes most of the typical
sections, such as introduction, methods, and results. These results are
initially based on simulated data with the same structure as the data
the authors expect to obtain from their experiments. For guidance on how
to simulate data, see Morris~et~al.~\citep{morrisUsingSimulationStudies2019},
Paxton~et~al.~\citep{paxtonMonteCarloExperiments2001}, and
Skrondal~\citep{skrondalDesignAnalysisMonte2000}, as well as the R packages
\href{https://cran.r-project.org/web/packages/simstudy/vignettes/simstudy.html}{\texttt{simstudy}},
\citep{simstudy} and
\href{https://personality-project.org/r/psych/help/sim.html}{\texttt{psych}},
\citep{psych}.

@@

\textls[+15]{The idea of submitting code as part of a preregistration is not new (e.g.~\citep{wichertsDegreesFreedomPlanning2016}). A prominent preregistration platform, \href{https://osf.io/}{The Open Science
Framework}, suggests submitting scripts alongside the preregistration of methods. In an informal literature search (we skimmed the first 300 results of Google Scholar with the keywords \texttt{\textls[+35]{("pre\ registration"\textbar{}"pre-registration"\textbar{}preregistration)\&(code\textbar{}script\textbar{}matlab\textbar{}}\linebreak python\textbar{}"R")}) we only found close to a dozen published articles that did include some form of script as part of their preregistration. Though the notion of preregistering code has been around for a while (cf.~\citep{steegenMeasuringCrowdAgain2014}), it has not gained much traction---perhaps because, to date, this has constituted an extra non-standard step in the research process. This tutorial integrates the preregistration of code into the reproducible research workflow by encouraging researchers to preregister the whole manuscript as a dynamic document.}

@@

We believe that pairing PAC with the workflow presented above offers
five advantages over classical preregistration. First, PAC is merely an
intermediate stage of the final manuscript, thus sparing authors from
writing, and editors and reviewers from evaluating, two separate
documents. Relatedly, writing the preregistration in the form of a
research article has the advantage that researchers are usually familiar
with this format. By contrast, a preregistration template is a novelty
for many. Second, PAC is a tool for study planning. A study can be
carried out more efficiently if all steps are documented clearly than
when every step is planned ad hoc. Third, PAC removes ambiguity
regarding the translation of verbal analysis plans into code. PAC is
more comprehensive by design because its completeness can be empirically
checked with simulated data. Evaluating the intended analysis code on
simulated data will help identify missing steps or ambiguous decisions.
PAC, therefore, minimizes undisclosed researchers degrees of freedom
more effectively than standard preregistration does
\citep{bakkerEnsuringQualitySpecificity2020, wichertsDegreesFreedomPlanning2016}.
Fourth, despite its rigor, PAC accommodates data-dependent decisions if
these can be formulated as code. Researchers can, for example, formulate
conditions (e.g., in the form of if-else-blocks) under which they prefer
one analysis type over the other. For example, if distributional
assumptions are not met, the code may branch out to employ robust
methods; or an analysis may perform automated variable selection
mechanisms before running the final model. Another example of
data-dependent decisions are more explorative analyses, i.e.,~explorative
factor analysis or machine learning. Decisions that do not lend
themselves to formulation in code, e.g.~visual inspection, must still be
described verbally or be treated as noted in the next section. Fifth,
deviations from the preregistration are clearly documented because they
are reflected in changes to the code, which are managed and tracked with
version control.

@@

Although researchers may use any form to preregister their planned
analyses (e.g., scripts), we suggest writing three functions for each
planned hypothesis: one to conduct the planned analysis, one to simulate
the expected data, and one to report the results. Using functions makes the
analysis more portable (i.e., it can easily be used for other datasets),
and facilitates repeated evaluation, as is the case in a simulation
study. The functions shown here do not contain executable code, but the
interested reader can find working functions in the {online
supplementary materials}
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation_funs.R} accessed on 11 October 2021) that power the example below.

@@

Ideally, these three functions can be composed to create a ``fake''
results section, e.g.~when composed to
\texttt{report\_analysis(planned\_analysis(simulate\_data()))} or
\texttt{simulate\_data()\ \%\textgreater{}\%\ planned\_analysis()\ \%\textgreater{}\%\ report\_analysis()}
outputs a results section.

@@

\begin{quote}
{Navigate to}
~\url{https://zenodo.org/login/ accessed on 11 October 2021} → Log in with GitHub
\end{quote}

@@

\begin{quote}
Log into zenodo.org → Account → {GitHub}~({\url{https://zenodo.org/account/settings/github/}})
\end{quote}

@@

\begin{quote}
{Navigate to}
 \url{https://zenodo.org/account/settings/github/}
\end{quote}

@@

To summarize, researchers need to write three functions,
\texttt{planned\_analysis()}, \texttt{simulate\_data()}, and
\texttt{report\_analysis()} and embed these into a manuscript that
serves as a preregistration in an uneditable online repository. After
they gathered the actual data, they can replace the simulated data,
render the dynamic manuscript (therefore run
\texttt{planned\_analysis()} on the actual data), and write the
discussion.

@@

Again, we propose a preregistration format that closely resembles a
classic journal article but uses simulated data and dynamic document
generation to create a document that starts out as a preregistration and
eventually becomes the final report. The complete preregistration source
is available in the {online supplementary material}
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/preregistration.Rmd} accessed on 11 October 2021). In this section, we show code excerpts of this
preregistration (formatted in monospace) and explain the rationale
behind them.

@@

We choose the following statistical procedure because many researchers
are familiar {with it}
~(The \emph{t}-test and Mann-Whitney-Wilcoxon test
  are arguably the most often used hypothesis tests (according to
 ~\citep{fagerlandTtestsNonparametricTests2012, hortonStatisticalMethodsJournal2005}
  reports that 26\% of all studies employed a \emph{t}-test and 27\% employed a
  rank-based alternative in the \emph{New England Journal of Medicine}
  in 2005). The analytical strategy presented here is, in fact,
  suboptimal in several respects (the assumption of measurement
  invariance is untested
 ~\citep{putnickMeasurementInvarianceConventions2016}, the effect size
  is underestimated in the presence of measurement error
 ~\citep{frostCorrectingRegressionDilution2000}, the effect size is
  overestimated for highly skewed distributions
 ~\citep{stonehouseRobustnessTestsCombined1998}). The interested reader
  can use the {provided code for the simulation}
~\mbox{(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R})} to verify that the \emph{t}-test provides unbiased
  effect sizes but the Mann-Whitney-Wilcoxon overestimates effect sizes
  with increasing sample size and skewness.):

@@

Together with the function \texttt{simulate\_data()} (not shown here),
the function \texttt{planned\_\linebreak analysis()} can be used to justify the
planned sample size. To that end, \texttt{simulate\_data()} is
repeatedly called with increased sample sizes and the proportion of
significant results (power) is recorded. The results for such a Monte
Carlo simulation for this example are visualized in {Figure~\ref{figure3}.}
 The code
for this power analysis can be found in the {online supplementary material}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R} accessed on 11 October 2021). The next snippet shows how we integrated the
results dynamically into the preregistration (the origin of the
R-variables \texttt{minn}, \texttt{choosen\_power}, and
\texttt{choosen\_d} is not shown).

@@

Readers can inspect and judge the changes for themselves on {GitHub}
\textls[-25]{(\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main\#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b})}.

@@

The example rendered as a {PDF file with real data}
(\url{https://github.com/aaronpeikert/repro-tutorial/files/7309455/preregistration.pdf} accessed on 11 October 2021) is available in the {online supplementary material}
(\url{https://github.com/aaronpeikert/repro-tutorial/releases/tag/v0.0.3.1-results} accessed on 11 October 2021). The changes we made since preregistering it can
be inspected on this {GitHub page}
(\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main\#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b} accessed on 11 October 2021).

@@

Increased automation is increasingly recognized as a means to improve
the research process~\citep{rouderMinimizingMistakesPsychological2019},
and therefore this workflow fits nicely together with other innovations
that employ automation, like machine-readable hypothesis tests
\citep{lakensImprovingTransparencyFalsifiability2021} or automated data
documentation~\citep{arslanHowAutomaticallyDocument2019}. Automated
research projects promise a wide range of applications, among them PAC
\citep[potentially to be submitted as a registered
report][]{nosekRegisteredReports2014, chambersWhatNextRegistered2019},
direct replication~\citep{simonsValueDirectReplication2014}, fully
automated living metanalysis~\citep{elliottLivingSystematicReviews2014},
executable research articles
\citep{elifesciencespublicationsELifeLaunchesExecutable2020}, and other
innovations such as the live analysis of born open data
\citep{rouderWhatWhyHow2016, kekecsRaisingValueResearch2019}.

@@

\texttt{repro}'s modular structure allows such alternative workflows,
though they have not yet been implemented. Depending on the demand by
users, we will implement some of them in \texttt{repro} and hope for
broad adoption of computational reproducibility in the near future.

@@

Supplementary Materials {All materials (i.e., the source code, all figures, and the data) that are neccesary for reproducing the submitted version of this article are availible at \url{https://github.com/aaronpeikert/repro-tutorial} and archived under \url{https://doi.org/10.5281/zenodo.5724454}}.

@@

\funding{This research received no external funding}

@@

% Reference 11
\bibitem[Knuth and Levy(1994)]{knuthCWEBSystemStructured}
Knuth, D.E.; Levy, S. \emph{The CWEB System of Structured Documentation}; Addison-Wesley Longman: \hl{Boston, USA, 1994.}

@@

% Reference 22
\bibitem[Ushey(2021)]{R-renv}
Ushey, K. Renv: Project Environments, 2021. \hl{R Package Version 0.13.2.}%MDPI: Please provide an available website and its accessed date.

% Reference 23
\bibitem[Wickham and Bryan(2021)]{usethis}
Wickham, H.; Bryan, J. Usethis: Automate Package and Project Setup, \hl{2021.}%MDPI: Please provide an available website and its accessed date.

>>>>

%=================================================================
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{5}
\pubyear{2021}
\copyrightyear{2021}
\externaleditor{Academic Editor: {Alexander Robitzsch}}
\datereceived{11 October 2021} 
\dateaccepted{25 November 2021} 
\datepublished{7 December 2021}
\hreflink{https://doi.org/} % If needed use \linebreak

@@

\AuthorCitation{Peikert, A.;  van Lissa, J.; Brandmaier, A.M.}
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Center for Lifespan Psychology---Max Planck Institute for Human Development, Lentzeallee 94, \mbox{14195 Berlin, Germany;} brandmaier@mpib-berlin.mpg.de\\
$^{2}$ \quad Humboldt-Universität zu Berlin, Unter den Linden 6, \mbox{10117 Berlin, Germany}\\
$^{3}$ \quad {Department} of Methodology \& Statistics---Utrecht {University}, {Faculty} of Social and Behavioral Sciences
, Heidelberglaan 8, 3584 CS Utrecht, The Netherlands; C.J.vanLissa@uu.nl\\
$^{4}$ \quad Open Science Community Utrecht, Heidelberglaan 8, 3584 CS Utrecht, The Netherlands\\
$^{5}$ \quad Max Planck UCL Centre for Computational Psychiatry and Ageing Research, \mbox{{Lentzeallee 94,
14195 Berlin, Germany, and London WC1B 5EH, UK}}\\
$^{6}$ \quad MSB Medical School Berlin, Rüdesheimer Str. 50, 14197 Berlin, Germany}

@@

Dynamic document generation integrates both steps. Through dynamic
document generation, code becomes an integral, although usually hidden,
part of the manuscript, complementing the verbal description and
allowing interested readers to gain a deeper understanding of the
contents
\citep{knuthCWEBSystemStructured, claerboutElectronicDocumentsGive1992}.
\texttt{R\ Markdown} uses \texttt{Markdown} for text formatting and R
(or other programming languages) for writing the statistical analysis.
\texttt{Markdown} is a lightweight text format in plain text with a
minimal set of reserved symbols for formatting instructions. This way,
\texttt{Markdown} does not need any specialized software for editing. It
is userfriendly (unlike, for example, \texttt{LaTeX}
\citep{lamportLATEXDocumentPreparation1994}), works well with version
control systems, and can be exported to various document formats, such
as HTML websites, a Microsoft Word document, a typeset PDF file (for
example, via LaTeX journal templates), or a Powerpoint presentation.
\texttt{Markdown} can be used for all sorts of academic documents,
ranging from simple sketches of ideas to scientific manuscripts
\citep{R-rticles} and presentations~\citep{revealjs}, or even résumés
\citep{vitae}. \texttt{R\ Markdown} extends regular \texttt{Markdown} by
allowing users to include R code chunks (in fact, arbitrary computer
code (\citep{xieMarkdownCookbook2020} Chapter 15, Chapter 15, Other
Languages)) into a \texttt{Markdown} document.
Upon rendering the document, the code blocks are executed, and their
output is dynamically inserted into the document. This allows the
creation of (conditionally) formatted text, statistical results, and
figures that are guaranteed to be up-to-date because they are created
anew every time the document is rendered to its output format (e.g.,
presentation slides or a journal article).
Xie et al.~\citep{xieMarkdownCookbook2020} provides an extensive yet practical
introduction to most features of \texttt{R\ Markdown}.

@@

\begin{figure}[H]
%\centering
\includegraphics[width=13.5cm]{Figures/nutshell.pdf}
\caption{Schematic illustration of the interplay of the four
components (in dashed columns) central to the reproducible workflow:
version control (\texttt{Git}), dependency tracking (\texttt{Make}),
software management (\texttt{Docker}), and dynamic document generation
(\texttt{R\ Markdown}). \texttt{Git} tracks changes to the project over
time. \texttt{Make} manages dependencies among the files.
\texttt{Docker} provides a container in which the final report is built
using dynamic document generation in \texttt{R\ Markdown}. Adapted from
Peikert and Brandmaier~\citep{Peikert2019} licensed under CC BY 4.0 
(\url{https://creativecommons.org/licenses/by/4.0} accessed on 4 December 2021).}
\label{figure1}
\end{figure}

@@

The first step is to install the required software. We assume that you
have installed R~(\citep{R-base} version 4.0.4) and RStudio
(\citep{rstudio} version 1.4) already but the tutorial will guide you in
detail through the installation of other necessary software with the
help of the R package {\texttt{repro}} 
(\url{https://github.com/aaronpeikert/repro} accessed on 4 December 2021)~\citep{R-repro}. In case you have either not installed R and RStudio or
are unsure if they are up-to-date, you might want to consult our
installation advice in the Online Supplementary Material
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md} accessed on 4 December 2021) that covers the installation of all software
necessary for this tutorial in three steps. The
{installation advice}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md} accessed on 11 October 2021) may also help Windows users who have problems installing
\texttt{Docker}.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  Text (prose; e.g., a scientific paper or presentation)
\item
  Executable code (e.g., analyses)
\item
  Metadata (e.g.,~title, authors, document format)
\end{enumerate}

@@

One advantage of this type of markup for formatting is that it can be
rendered to many different output formats---both in terms of file types,
like \texttt{.docx}, \texttt{.html}, \texttt{.pdf}, and in terms of
style, e.g.~specific journal requirements. For social scientists, the
\href{https://github.com/crsh/papaja}{\texttt{papaja}} package~\citep{papaja} may be relevant, as it produces manuscripts that follow
the American Psychological Association formatting requirements
\citep{apa7}. \texttt{R\ Markdown} files are plain text, which is more
suitable for version control using \texttt{Git} than binary files
generated by some word processors. Some users might find it easier to
activate the ``Visual Editor'' of RStudio ({[}Ctrl{]} + {[}Shift{]} +
{[}F4{]} or click on the icon that resembles drawing materials or a
compass in the upper right corner of the \texttt{R\ Markdown} document),
which features more graphical elements like a traditional word processor
but still creates an \texttt{R\ Markdown} underneath with all of its
flexibility. The visual editor has some additional benefits, such as
promoting best practices (for example, each sentence should be written
on a new line, which makes it easier to track changes across versions)
and improving the generation of citations and references to tables and
figures.

@@

The hotkey {[}Control{]} + {[}Alt{]} + {[}i{]} inserts a block of code in
the file. The results of code enclosed in such backticks will be
dynamically inserted into the document (depending on specific settings).
This means that whenever you render the \texttt{R\ Markdown} to its
intended output format, the code will be executed and the results
updated. The resulting output document will be static, e.g., a pdf
document, and can be shared wherever you like, e.g., on a preprint
server.

@@

The workflow described in this paper facilitates a rigorous solution to
this problem: Instead of describing the analysis in prose, researchers
include the code required to conduct the analysis in the
preregistration. We term this approach of writing and publishing code at
the preregistration stage \emph{Preregistration as Code (PAC)}. PAC has
the potential to eliminate undisclosed researchers degrees of freedom to
a much greater extent than, e.g., preregistration templates. Moreover,
it reduces overhead by removing the need to write a separate
preregistration and manuscript. For PAC, researchers can write a
reproducible, dynamically generated draft of their intended manuscript
at the preregistration stage. This already includes most of the typical
sections, such as introduction, methods, and results. These results are
initially based on simulated data with the same structure as the data
the authors expect to obtain from their experiments. For guidance on how
to simulate data, see Morris~et~al.~\citep{morrisUsingSimulationStudies2019},
Paxton~et~al.~\citep{paxtonMonteCarloExperiments2001}, and
Skrondal~\citep{skrondalDesignAnalysisMonte2000}, as well as the R packages
\href{https://cran.r-project.org/web/packages/simstudy/vignettes/simstudy.html}{\texttt{simstudy}},~\citep{simstudy} and
\href{https://personality-project.org/r/psych/help/sim.html}{\texttt{psych}},
\citep{psych}.

@@

\textls[+15]{The idea of submitting code as part of a preregistration is not new (e.g.,~\citep{wichertsDegreesFreedomPlanning2016}). A prominent preregistration platform, \href{https://osf.io/}{The Open Science
Framework}, suggests submitting scripts alongside the preregistration of methods. In an informal literature search (we skimmed the first 300 results of Google Scholar with the keywords \texttt{\textls[+35]{("pre\ registration"\textbar{}"pre-registration"\textbar{}preregistration)\&(code\textbar{}script\textbar{}matlab\textbar{}}\linebreak python\textbar{}"R")}) we only found close to a dozen published articles that did include some form of script as part of their preregistration. Though the notion of preregistering code has been around for a while (cf.~\citep{steegenMeasuringCrowdAgain2014}), it has not gained much traction---perhaps because, to date, this has constituted an extra non-standard step in the research process. This tutorial integrates the preregistration of code into the reproducible research workflow by encouraging researchers to preregister the whole manuscript as a dynamic document.}

@@

We believe that pairing PAC with the workflow presented above offers
five advantages over classical preregistration. First, PAC is merely an
intermediate stage of the final manuscript, thus sparing authors from
writing, and editors and reviewers from evaluating, two separate
documents. Relatedly, writing the preregistration in the form of a
research article has the advantage that researchers are usually familiar
with this format. By contrast, a preregistration template is a novelty
for many. Second, PAC is a tool for study planning. A study can be
carried out more efficiently if all steps are documented clearly than
when every step is planned ad hoc. Third, PAC removes ambiguity
regarding the translation of verbal analysis plans into code. PAC is
more comprehensive by design because its completeness can be empirically
checked with simulated data. Evaluating the intended analysis code on
simulated data will help identify missing steps or ambiguous decisions.
PAC, therefore, minimizes undisclosed researchers degrees of freedom
more effectively than standard preregistration does
\citep{bakkerEnsuringQualitySpecificity2020, wichertsDegreesFreedomPlanning2016}.
Fourth, despite its rigor, PAC accommodates data-dependent decisions if
these can be formulated as code. Researchers can, for example, formulate
conditions (e.g., in the form of if-else-blocks) under which they prefer
one analysis type over the other. For example, if distributional
assumptions are not met, the code may branch out to employ robust
methods; or an analysis may perform automated variable selection
mechanisms before running the final model. Another example of
data-dependent decisions are more explorative analyses, i.e.,~explorative
factor analysis or machine learning. Decisions that do not lend
themselves to formulation in code, e.g.,~visual inspection, must still be
described verbally or be treated as noted in the next section. Fifth,
deviations from the preregistration are clearly documented because they
are reflected in changes to the code, which are managed and tracked with
version control.

@@

Although researchers may use any form to preregister their planned
analyses (e.g., scripts), we suggest writing three functions for each
planned hypothesis: one to conduct the planned analysis, one to simulate
the expected data, and one to report the results. Using functions makes the
analysis more portable (i.e., it can easily be used for other datasets),
and facilitates repeated evaluation, as is the case in a simulation
study. The functions shown here do not contain executable code, but the
interested reader can find working functions in the {online
Supplementary Materials}
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation_funs.R} accessed on 11 October 2021) that power the example below.

@@

Ideally, these three functions can be composed to create a ``fake''
results section, e.g.,~when composed to
\texttt{report\_analysis(planned\_analysis(simulate\_data()))} or\\
\texttt{simulate\_data()\ \%\textgreater{}\%\ planned\_analysis()\ \%\textgreater{}\%\ report\_analysis()}
outputs a results section.

@@

\begin{quote}
{Navigate to}
~\url{https://zenodo.org/login/} accessed on 11 October 2021 → Log in with GitHub
\end{quote}

@@

\begin{quote}
Log into zenodo.org → Account → {GitHub}~({\url{https://zenodo.org/account/settings/github/} accessed on 4 December 2021 })
\end{quote}

@@

\begin{quote}
{Navigate to}
 \url{https://zenodo.org/account/settings/github/} accessed on 4 December 2021
\end{quote}

@@

To summarize, researchers need to write three functions,
\texttt{planned\_analysis()}, \\ \texttt{simulate\_data()}, and
\texttt{report\_analysis()} and embed these into a manuscript that
serves as a preregistration in an uneditable online repository. After
they gathered the actual data, they can replace the simulated data,
render the dynamic manuscript (therefore run
\texttt{planned\_analysis()} on the actual data), and write the
discussion.

@@

Again, we propose a preregistration format that closely resembles a
classic journal article but uses simulated data and dynamic document
generation to create a document that starts out as a preregistration and
eventually becomes the final report. The complete preregistration source
is available in the {online Supplementary Material}
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/preregistration.Rmd} accessed on 11 October 2021). In this section, we show code excerpts of this
preregistration (formatted in monospace) and explain the rationale
behind them.

@@

We choose the following statistical procedure because many researchers
are familiar {with it}
~(The \emph{t}-test and Mann-Whitney-Wilcoxon test
  are arguably the most often used hypothesis tests (according to
 ~\citep{fagerlandTtestsNonparametricTests2012, hortonStatisticalMethodsJournal2005}
  reports that 26\% of all studies employed a \emph{t}-test and 27\% employed a
  rank-based alternative in the \emph{New England Journal of Medicine}
  in 2005). The analytical strategy presented here is, in fact,
  suboptimal in several respects (the assumption of measurement
  invariance is untested
 ~\citep{putnickMeasurementInvarianceConventions2016}, the effect size
  is underestimated in the presence of measurement error
 ~\citep{frostCorrectingRegressionDilution2000}, the effect size is
  overestimated for highly skewed distributions
 ~\citep{stonehouseRobustnessTestsCombined1998}). The interested reader
  can use the {provided code for the simulation}
~{(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R} accessed on 4 December 2021)} to verify that the \emph{t}-test provides unbiased
  effect sizes but the Mann-Whitney-Wilcoxon overestimates effect sizes
  with increasing sample size and skewness.):

@@

Together with the function \texttt{simulate\_data()} (not shown here),
the function \texttt{planned\_\linebreak analysis()} can be used to justify the
planned sample size. To that end, \texttt{simulate\_data()} is
repeatedly called with increased sample sizes and the proportion of
significant results (power) is recorded. The results for such a Monte
Carlo simulation for this example are visualized in {Figure~\ref{figure3}.}
 The code
for this power analysis can be found in the {online Supplementary Material}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R} accessed on 11 October 2021). The next snippet shows how we integrated the
results dynamically into the preregistration (the origin of the
R-variables \texttt{minn}, \texttt{choosen\_power}, and
\texttt{choosen\_d} is not shown).

@@

Readers can inspect and judge the changes for themselves on {GitHub}
\textls[-25]{(\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main\#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b} accessed on 4 December 2021)}.

@@

The example rendered as a {PDF file with real data}
(\url{https://github.com/aaronpeikert/repro-tutorial/files/7309455/preregistration.pdf} accessed on 11 October 2021) is available in the {online Supplementary Material}
(\url{https://github.com/aaronpeikert/repro-tutorial/releases/tag/v0.0.3.1-results} accessed on 11 October 2021). The changes we made since preregistering it can
be inspected on this {GitHub page}
(\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main\#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b} accessed on 11 October 2021).

@@

Increased automation is increasingly recognized as a means to improve
the research process~\citep{rouderMinimizingMistakesPsychological2019},
and therefore this workflow fits nicely together with other innovations
that employ automation, like machine-readable hypothesis tests
\citep{lakensImprovingTransparencyFalsifiability2021} or automated data
documentation~\citep{arslanHowAutomaticallyDocument2019}. Automated
research projects promise a wide range of applications, among them PAC
(\citep{nosekRegisteredReports2014, chambersWhatNextRegistered2019} potentially to be submitted as a registered
report),
direct replication~\citep{simonsValueDirectReplication2014}, fully
automated living metanalysis~\citep{elliottLivingSystematicReviews2014},
executable research articles
\citep{elifesciencespublicationsELifeLaunchesExecutable2020}, and other
innovations such as the live analysis of born open data
\citep{rouderWhatWhyHow2016, kekecsRaisingValueResearch2019}.

@@

\texttt{repro}'s modular structure allows such alternative workflows,
though they have not yet been implemented. Depending on the demand by
users, we will implement some of them in \texttt{repro} and hope for
broad adoption of computational reproducibility in the near~future.

@@

\supplementary{All materials (i.e., the source code, all figures, and the data) that are neccesary for reproducing the submitted version of this article are availible at \url{https://github.com/aaronpeikert/repro-tutorial} and archived under \url{https://doi.org/10.5281/zenodo.5724454} (accessed on 4 December 2021).}

@@

\funding{This research received no external funding.}

@@

% Reference 11
\bibitem[Knuth and Levy(1994)]{knuthCWEBSystemStructured}
Knuth, D.E.; Levy, S. \emph{The CWEB System of Structured Documentation}; Addison-Wesley Longman: {Boston, MA, USA, 1994.}

@@

% Reference 22
\bibitem[Ushey(2021)]{R-renv}
Ushey, K. Renv: Project Environments, 2021. {R Package Version 0.13.2.} Available online: \url{https://rstudio.github.io/renv/articles/renv.html} (accessed on 4 December 2021).%MDPI: Please provide an available website and its accessed date.

% Reference 23
\bibitem[Wickham and Bryan(2021)]{usethis}
Wickham, H.; Bryan, J. Usethis: Automate Package and Project Setup. {2021.} Available online: \url{https://usethis.r-lib.org} (accessed on 4 December 2021).%MDPI: Please provide an available website and its accessed date.
